Towards a universal-dependency treebank for Kazakh

### 2015-06-18 2015-turklang-kazdep/paper.tex
more stuff and bib
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60811 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{multirow}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}

\usepackage{natbib}

\usepackage{times}

\title{Towards a universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA}

\keywords{Kazakh, treebank, dependency grammar, universal dependency}

@@

@@

>>>>

\usepackage{fontspec}
\usepackage{xunicode}

\usepackage{multirow}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}

\usepackage{natbib}
\bibdata{paper}

%\usepackage{times}
\setmainfont{Times New Roman}

\title{Towards a universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA\footnote{Corresponding author.  E-mail address: jonwashi@indiana.edu}}

\keywords{Kazakh; treebank; dependency grammar; universal dependency}

@@

\citet{hargle}

@@

\bibliographystyle{apa}
\bibliography{paper}
